---
title: "Testing look up methods"
output:
  html_document:
    df_print: paged
---

Source: https://appsilon.com/fast-data-lookups-in-r-dplyr-vs-data-table/

# Prep
```{r, results='hide', message=FALSE, warning=FALSE }
library(geographr)
library(tidyverse)
library(data.table)

options(scipen = 999)
```

Functions for calculating average times for code
```{r}
time <- function(...) {
  time_measurement <- system.time(eval(...))
  time_measurement[["user.self"]]
}

benchmark <- function(..., n = 50) {
  times <- replicate(n, ...)
  c(min = min(times), max = max(times), mean = mean(times))
}
```

Loading in lookup table and search terms
```{r}
lookupdf <- lookup_postcode_oa_11_lsoa_11_msoa_11_lad_20 |>
  select(postcode, msoa_11_code)

postcodes_to_find <- c("E16AN", "NE11DE")
```

# Hashtables 

## Create environment

```{r}
environment_source <- setNames(
  object = as.list(lookupdf$msoa_11_code),
  nm = lookupdf$postcode
)


start_time <- Sys.time()
my_env <- as.environment(environment_source)
end_time <- Sys.time()

end_time - start_time
```

Could also try `list2env()` for creating environment and see if any faster from [here](https://riptutorial.com/r/example/18339/environments-as-hash-maps). 

```{r}
start_time <- Sys.time()
my_env2 <- list2env(
  setNames(
    object = as.list(lookupdf$msoa_11_code),
    nm = lookupdf$postcode
  ),
  envir = NULL,
  hash = TRUE
)
end_time <- Sys.time()

end_time - start_time
```


## Testing search code 

Search single term
```{r}
my_env[["E16AN"]]
```

Search multiple terms have to use `mget`
```{r}
mget(postcodes_to_find, envir = my_env)
```

Just extract the MSOAs 
```{r}
mget(postcodes_to_find, envir = my_env) |>
  unname() |>
  unlist()
```

## Testing time 

Search time for single term
```{r}
benchmark({
  time(
    my_env[["E16AN"]]
  )
})
```

Test search time for multiple terms
```{r}
benchmark({
  time(
    mget(postcodes_to_find, envir = my_env) |>
      unname() |>
      unlist()
  )
})
```


# Dplyr

```{r}
benchmark({
  time(
    lookupdf |>
      filter(postcode %in% postcodes_to_find)
  )
})
```

# Datatable 

```{r}
lookupdf_datatable <- data.table(lookupdf)
```

Search time for single term
```{r}
benchmark({
  time(
    lookupdf_datatable[postcode == "E16AN", ]
  )
})
```


```{r}
lookupdf_datatable[postcode %in% postcodes_to_find, ]
```

Search time for multiple terms
```{r}
benchmark({
  time(
    lookupdf_datatable[postcode %in% postcodes_to_find, ]
  )
})
```


# Datatable ordered indexes

```{r}
lookupdf_datatable_ord <- lookupdf_datatable
time(setkey(lookupdf_datatable_ord, postcode))
```

```{r}
lookupdf_datatable_ord
```

Test code
```{r}
lookupdf_datatable[.("E16AN"), nomatch = 0L]
```

```{r}
lookupdf_datatable[.(postcodes_to_find), nomatch = 0L]
```

Search time for single term
```{r}
benchmark({
  time(
    lookupdf_datatable[.("E16AN"), nomatch = 0L]
  )
})
```

Search time for multiple terms
```{r}
benchmark({
  time(
    lookupdf_datatable[.(postcodes_to_find), nomatch = 0L]
  )
})
```
 
# Other sources
 
* [Environments - Advanced R](http://adv-r.had.co.nz/Environments.html)
* [Hashtable performance](https://jeffreyhorner.tumblr.com/post/116325104028/hash-table-performance-in-r-part-ii-in-part-i) 
* [Benchmarking of hashtables](https://blog.dominodatalab.com/a-quick-benchmark-of-hashtable-implementations-in-r)
 
