---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rvest)
library(robotstxt)  
```

# UK Power Networks ----
https://www.ukpowernetworks.co.uk/internet/en/terms-and-conditions/:

You are permitted to download and print content from our site solely for your own internal business purposes and/or personal use. Our site content must not be copied or reproduced, used or otherwise dealt with for any other reason. 

```{r}
url <- "https://www.ukpowernetworks.co.uk/power-cut/list"
```

Use functions to check if scraping allowed https://github.com/ropensci/robotstxt

```{r}
paths_allowed(domain = "https://www.ukpowernetworks.co.uk", paths = "/power-cut/")
paths_allowed(domain = "https://www.ukpowernetworks.co.uk", paths = "/power-cut/list")
```

```{r}
html <- read_html(url)
```

```{r}
html
```

```{r}
body_nodes <- html %>% 
  html_node("body") %>% 
  html_children()

body_nodes
```



class="table table-responsive dataTable no-footer"

```{r}
tidy_power_data <- html %>%
  html_table() 
```

```{r}
tidy_power_data
```


# Other provider tables 
https://www.spenergynetworks.co.uk/pages/power_cuts_list.aspx
https://powertrack.ssen.co.uk/powertrack (table at side)

